upwell_IDX

### 2019-08-21 SST_patterns.Rmd
updated

# Using the upwelling metrics created in `upwell.IDX.Rmd` Identify when upwelling occurs at the particular site. 
# Is this upwelling event seen throughout the different distances from the coastline
# Using CMC, MUR, OISST and SACTN_US to determine wether the upwelling events detected is present in each of the datasets

>>>>

# Using the upwelling metrics created in `upwell.IDX.Rmd` Identify when upwelling occurs at the particular site. 
# Is this upwelling event seen throughout the different distances from the coastline
# Using CMC, MUR, OISST and SACTN_US to determine wether the upwelling events detected are present in each of the datasets

### 2019-08-21 upwell_IDX.Rmd
updated

##### Upwelling #####
# Min duration for an upwelling event - 1day and threshold -1. Upwelling can over within a few hours, but given that we have daily data - upwelling has a minimum duration of 1 day
# Seasonal upwelling. Upwelling seasons are summer and spring
# Did the wind intensify? This is usually done by taking first third of the dataset and the last thid of the dataset and doing a t-test on this
# Strong south easterly winds lead to a stronger upwelling event

>>>>

##################### Upwelling ######################
# Min duration for an upwelling event - 1day and threshold -1. Upwelling can over within a few hours, but given that we have daily data - upwelling has a minimum duration of 1 day
# Seasonal upwelling. Upwelling seasons are summer and spring
# Did the wind intensify? This is usually done by taking first third of the dataset and the last thid of the dataset and doing a t-test on this
# Strong south easterly winds lead to a stronger upwelling event
##############################################
